Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2017-02-14 R0V0.tex
Modify abstract and introduction

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
In this paper, large-scale input-affine nonlinear systems are considered. The problem is the design of distributed controllers for this class of network systems. Although control-Lyapunov functions are the natural candidates to design feedback laws, in this case, numerical methods employed to construct for these functions usually lead to a non-convex optimization problem. Moreover, it may require to verify the positiveness of a function with, at least, $n^2$ elements. In this paper, control-contraction metrics (CCMs) are employed to design controllers with suitable distributed structures. By exploiting sparsity, the number of verifications needed can be made smaller, as the search of CCMs is formulated as a distributed semidefinite program. An example illustrates the approach for a network system.
\end{abstract}

@@

\mypara Over the years, the improvements on distance communication and cheaper computation platform have allowed the development of large-scale interconnected systems such as smart grids, smart sensor networks, smart manufacturing plants and intelligent transportation systems. One of the main characteristic of these systems is the capacity of being autonomous. Most of current controller algorithms written to render technologies automatic is based on the assumption that the system will operate ``near'' to a prescribed set point. In other words, the system will designed fixed behavior. This assumption imposes severe limitations for system, as large excursions are not allowed, in general. For instance, large variations on smart grids are not allowed and manufacturing plants tend to synthesize only a fixed range of goods. To render these systems more flexible, i.e., allowing large excursions a controller algorithm that takes into account a more complex behavior is needed.

\mypara In terms of mathematical systems theory, the difference between a system operating in a set point and operating in a much larger region lies in the type of equations that describes the system behavior. For the former, the system is described by linear equation while, for the latter, by a nonlinear one. 
\todo[inline]{Continue with difficulties to design nonlinear controller.}
Methods for the design of distributed controllers for large-scale systems have developed different techniques, according to the vector field that describes the system structure. For linear systems, controller design problems are often translated in terms of optimization.

\mypara Numerical methods to design linear controllers include $H_\infty$ optmization \cite{Doyleetal1992} and LQR \cite{Hespanha:2009}. The design problems are usually formulated in terms of linear matrix inequalities (LMIs) and semidefinite programming \cite{Boyd1994,DullerudPaganini2000}. In the case of nonlinear systems, design approaches are generally analytic and include high-gain  \cite{GrognardSepulchreBastin1999}, backstepping \cite{Krstic1995}, and forwarding \cite{MazencPraly96}. These methods depend on the structure of the vector field and may fail to be applied when appropriate conditions are not met \cite{SteinShiromoto2013a}.

\mypara For systems described by input-affine differential equations,  the existence of a control-Lyapunov function (CLF) satisfying the so-called \emph{small control property} provides a ``universal'' formula for a stabilizing feedback law  \cite{Sontag1983,Sontag1989a}. However, by the time that this paper was submitted, systematic methods for the search of a CLF were known only for particular systems within this class (see, for instance, \cite{MazencMalisoff2006}). In addition to the lack of a general systematic approach, the search for a CLF in terms of numerical optimization leads to a problem that is not necessarily convex nor connected \cite{Rantzer:2001}.

\mypara An alternative to CLFs is provided by the so-called control-contraction metrics (CCMs). One of the main advantages of CCMs over CLFs is that the feedback law is obtained by solving a convex optimization problem \cite{Manchester2014a}.

\mypara One of the drawbacks of numerical methods is that, when the system under consideration has a large number of states, it may require a large memory size. This is due to the fact that the stability verification of a linear system with $n$ states may require a function with $n^2$ terms (see \cite{Rantzer2015} for the case of linear systems and Lyapunov functions). In general, the case is worse, for nonlinear systems.

\mypara Large-scale systems may appear in the form of interconnection of smaller components, for example, in applications such as traffic networks \cite{CanudasdeWitMorbidiLeonOjedaEtAl2015}, pipe networks \cite{Persis2011a} and sensor networks \cite{Pajic2011}. For such systems, a property often desired is the ability to synthetize controllers with particular structures (see \cite{Siljak1991,Bai2011} for distributed controllers).

\mypara In terms of semidefinite programming, the problem of design controllers having an arbitrary structure is known to be NP-hard \cite{BlondelTsitsiklis1997,Tanaka2011}, for linear systems. Consequently, for nonlinear systems the problem is very challenging.

\mypara In the case of linear systems whose solutions evolve in the positive orthant (positive systems), the problem of design a structured stabilizing feedback law has been addressed in \cite{Tanaka2011}. Also, the authors show that the existence of such a controller is equivalent to the existence of Lyapunov function with a diagonal structure. The importance of this result for large-scale systems is highlighted in \cite{Rantzer2015}, where sparsity is explored to solve linear programs.

\mypara For nonlinear systems, the design of structured controllers could be simplified by choosing structured control-Lyapunov functions (see \cite{Dirr2015} and references therein). However, the search for a general control-Lyapunov function is a non-trivial problem by itself (see \cite{MalisoffMazenc2009} for the search of Lyapunov functions). The case can be even worse, when structural constraints are imposed.

\mypara For this reason, the structured design of feedback laws for nonlinear systems is investigated with CCMs satisfying structural constraints. The systems under consideration are continuously differentiable and affine in the input. One of the key elements employed to design these controllers is the concept of a Riemannian metric (see the definition below) which is employed, similarly to Lyapunov functions, to measure the exponential convergence of pairs of solutions. Employing CCMs that can be decomposed into the sum of smaller elements, the design of a structured feedback law allowing exponential convergence of solutions is obtained in two steps.

@@

\mypara Other works related to analysis under structural constraints to achieve exponential convergence of solutions do exist in the literature. For contraction analysis, see \cite{Aminzare2014a} for analysis according to different network topologies and \cite{Andrieu2016} for transversal contraction analysis. This paper contrast with these works mainly in two points: 1) A  methodology for the design of structured controllers is proposed; 2) Due the formulation of the stabilization problem as a convex optimization problem, an explicit formula of a structured controller is obtained.

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
In this paper, large-scale input-affine nonlinear systems are considered. The problem is the design of distributed controllers for this class of network systems. Although control-Lyapunov functions are the natural candidates to design feedback laws, in this case, the construction of these functions is a non-convex optimization problem. Moreover, it may require to verify the positiveness of a function with, at least, $n^2$ elements. In this paper, control-contraction metrics (CCMs) are employed to design controllers with suitable distributed structures. By utilizing a separable structure, the number of verifications needed can be made smaller, as the search of CCMs is formulated as a distributed semidefinite program. An example illustrates the approach for a network system.
\end{abstract}

@@

\mypara Over the years, improvements on distance communication and cheaper computation platforms have allowed the development of large-scale interconnected systems such as smart grids, sensor networks \cite{Pajic2011}, smart manufacturing plants and traffic networks \cite{CanudasdeWitMorbidiLeonOjedaEtAl2015} and pipe networks \cite{Persis2011a}. One of the main characteristic of these systems is the capacity of being autonomous. Most of current control algorithms are based on the assumption that the system will operate ``near'' to a prescribed set point. Consequently, the system is designed to have fixed behavior. This assumption imposes severe limitations for system, as large excursions are not allowed, in general. For instance, large power variations on smart grids (e.g., when renewable sources of energy are taken into account) are not allowed and manufacturing plants tend to synthesize only a fixed range of goods. To render these systems more flexible, i.e., allowing large excursions a controller algorithm that takes into account a more complex behavior is needed.

\mypara In terms of control theory, the difference between a system operating in a set point and operating in a much larger region lies in the type of equation that describes the system behavior. In the former, the system is described by linear equation while, in the latter, by a nonlinear one. In general, controller design methods for nonlinear systems require the knowledge of a \emph{Lyapunov function}. The search of Lyapunov functions for this class of systems is a non-trivial problem by itself, as no general methodology exists. Another drawback of Lyapunov functions is the fact that they are defined with respect to a particular set point. In case of large excursions, it is more appropriate to define a function depending of the distance between set points. Even if a Lyapunov function is known, no general methodology is known to design distributed feedback laws for nonlinear systems. Thus, existing approaches are, in general, \emph{ad-hoc}. When the design of distributed controllers is considered, the situation is even worse as the problem is known to be, at least, NP-hard \cite{BlondelTsitsiklis1997,Tanaka2011}.

\mypara  An alternative method, called control contraction method (CCM), provides an algorithm in which nonlinear feedback laws are designed based on solving a convex optimization problem  \cite{Manchester2014a}. The main challenge with this methodology is that, when the system under consideration has a large number of states, it may require a large memory amount. This is due to the fact that the stability verification of a linear system with $n$ states may require a function with, at least, $n^2$ terms (see \cite{Rantzer2015} for the case of linear systems and Lyapunov functions).

\mypara One of the key elements employed to design these controllers is the concept of a Riemannian metric (see the definition below) which is employed, similarly to Lyapunov functions, to measure the exponential convergence of pairs of solutions to each other. Employing CCMs that can be decomposed into the sum of smaller elements, the design of a distributed feedback law allowing exponential convergence of solutions is obtained in two steps.

@@

\mypara Other works related to analysis under structural constraints to achieve exponential convergence of solutions do exist in the literature. For contraction analysis, see \cite{Aminzare2014a} for analysis according to different network topologies and \cite{Andrieu2016} for transversal contraction analysis. This paper contrast with these works mainly in two points: 1) A  methodology for the design of structured controllers is proposed; 2) Due the formulation of the stabilization problem as a convex optimization problem, an explicit formula of a structured controller is obtained. A particular case of this paper has also been published in \cite{SteinShiromotoManchester2016}. In contrast to this paper, more general conditions to design the distributed controller (cf. Corollary~\ref{cor:main result}) and a methodology to distribute the computation of the feedback law are given.
